Lensing

### 2015-02-24 Papers/ms.tex
Starting to discuss RJObject

In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. The source and the lens can be built up from a moderate
number of simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is dark. For the lens, if
we are interested in detecting and measuring the properties of dark
substructures, a superposition of an unknown number of ``blobs'' is the
relevant model.

@@

\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
Bayesian Analysis, submitted. ArXiv: 1411.3921

>>>>

In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. The source and the lens can be built up from a moderate
number of simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is dark.

For the lens, if we are interested in detecting and measuring the properties of
dark substructures, a superposition of an unknown number of ``blobs'' is the
relevant model. In addition, if we want to constrain the ``mass function'' of
these blobs, we will need a hierarchical model which specifies the probability
distribution for the masses, given some hyperparameters.

Computing the posterior distribution over the parameters of such a model
requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
of possible sources and lenses. In a recent paper,

@@

\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
preprint. ArXiv: 1411.3921
